Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-06-25 _tex/paper2.tex
Built site for gh-pages

>>>>

\section{Conclussion}\label{sec-conclussion}

This paper underscores the need to extend Thurstone's theory to meet the
demands of contemporary empirical CJ research. It specifically advocates
for the development of bespoke CJ models aligned with the underlying
data-generating processes of specific CJ assessment designs, as these
models have the potential to strengthen the robustness of trait
estimates and the clarity of inferences. The work also outlines a clear
trajectory for advancing CJ research in both theoretical and applied
domains. Finally, the study also lays the groundwork for broader
applications, encouraging researchers across the social sciences to
adopt more robust and interpretable methodologies.
